Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-10-06 LaTeX_paper/paper.tex
finish review of section 6

\subsection{Splitting The Pieces}
As introduced in section~\ref{document:splitter}, the first step to solve a puzzle
is to split an image composed of many pieces into individual ones.
This is relatively straightforward, and can be done with the following steps:

\begin{itemize}
  \item Apply a threshold and transform an RGB image into a binary mask.
  \item Find all individual Blobs
  (a Blob is just set of connected pixels with the same color) and for each one:

@@

The next step following the general template~\ref{document:splitter}
is to split a pieces into
his 4 sides, this could be done with the following steps:

@@

  \item \textbf{Remove the holes from the piece:}\newline
  To do so the program computes the convex hull of the piece~\ref{fig:s_s_ch},
  then calculates the difference between the convex hull and the original image,
  and obtains an image with the “filler areas”~\ref{fig:fig:s_s_og_minus_ch}.
  These filler areas have very different shapes,
  depending on what has generated them (a “hole” or a “knob” in the piece).
  So they can be classified, and added to the original piece only if
  they are generated by a hole, obtaining an image without holes~\ref{fig:s_s_no_holes}.

  \item \textbf{Remove the knobs from he piece}\newline
  To do so the image without holes gets eroded~\ref{fig:s_s_erosion} and then dilated~\ref{fig:s_s_dilatation}.
  This generates an image that resembles the original one, but has no knobs.
  Then the program finds the pixels that are white in the image without holes,
  but not in the image that has been eroded and dilated.
  This generates a set of Blobs~\ref{fig:s_s_no_holes_minus_expansion},
  but again, the shape of one blob is very different depending on what has generated it
  (an “angle” or a “knob”), so they can be classified.
  Then the program removes from the image with no holes all the pixels that are
  close to a Blob generated by a knob, obtaining an image without knobs and holes~\ref{fig:s_s_no_knobs}.

  \item \textbf{Find the coordinates of the four corners}\newline
  To find the coordinates of the corners, the program uses a tree steps approximation.
  It initially finds the minimum enclosing rectangle,
  and uses the coordinates of the corners of the rectangle
  as first approximation~\ref{fig:s_s_min_enc_rec}.\newline
  As a second approximation it takes,
  from the white pixels that are close to the first approximation,
  the pixel that has the most black pixels within a certain distance.
  Then it considers only the pixels that are within a certain
  distance of the second approximation, and finds the minimum
  enclosing triangle of sed pixels~\ref{fig:s_s_min_enc_triangle}.\newline
  The corner of the triangle that is closest to the second
  approximation is the third and final approximation
  of the corner of the piece.
  The position of the four corners can be seen in image~\ref{fig:s_s_corners_found}.

  \item \textbf{Split each side using the previously found coordinates.}\newline
	Once the program has found the four coordinates of the corners, to obtain each
  side. An example of a single side can be seen in image~\ref{fig:s_s_a_piece_side}.
\end{itemize}

@@

\subsection{Comparing The Sides}\label{document:my_comparator}
The last step needed before it is possible to start working on
a solver algorithm, is to compare the sides that have been
generated by the previous step.\newline
In order to generate a compatibility shore,
the program compute the following steps:

\begin{itemize}
  \item For each side, it considers only the border, and it makes the border thicker.
  \item It puts two sides attached to each other using the coordinates of the corners (In the same way a human would do to test if two pieces fit together).
  \item It calculates the “Or Area”; that is, the number of pixels that belong to the border of one side or the other.
  \item It calculates the “And Area”; that is, the number of pixels that belong to the border of both sides.
  \item It calculates the final shore, which is defined as: \(Shore = \frac{And \space Area}{Or \space Area}\), and goes from 0 to 1.
\end{itemize}

@@

\section{Applying Already Existing Algorithms To The Real World}
Now that the setup is completed, it is possible to test the already existing
algorithms with real world puzzles, to see if they can work. For this test,
the fist algorithm~\ref{document:GCL} has been chosen, because the paper is full of detail.
In particular it had some information about the accuracy of the algorithm in
function to the corruption rate, which are essential for this analysis.

The tests that have been conducted have shown that our comparator algorithm~\ref{document:my_comparator}
and the “Graph Connection Laplacian” solution~\ref{document:GCL} are not compatible with each other.
A proof for this claim follows.

@@

This section will provide a proof for the incompatibility of
the two algorithms mentioned above.
\newline
The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\ref{document:GCL} takes as input a binary value,
which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.
\subsubsection{Input Data}
To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:

\begin{itemize}
  \item \textbf{match\%:}\newline
  The probability that 2 random sides match.

  \item \textbf{correct combination match\% (or c.c match\%):}\newline
  The probability that 2 sides match given that in the correct puzzle
  solution they actually are close to each other. ideally this should be 1.

  \item \textbf{limit match\%:}\newline
  Given that this measure has been taken on a 16 piece puzzle,
  the match\% is highly influenced by the correct piece matching.
  With a bigger puzzle the match\% would be lower.
  Limit match\% is an approximation of what the match\%
  would be in the limit for \(N \rightarrow + \infty\) (where N is the number of pieces).
  This value is obtained by subtracting to match\%
  the probability of choosing randomly the correct side,
  multiplied by the probability that the comparison returns true
  (which is c.c match\%). ideally this should be almost zero.
  \[limit \: math\% = math\% - \frac{c.c. \: mathc\%}{16 \times 4}\]

  \item \textbf{corruption rate:}\newline
  Is defined as: \(1-\sqrt{c.c \: match\%}\). ideally this should be 0.

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{FFE599}}c 
  >{\columncolor[HTML]{B6D7A8}}c 
  >{\columncolor[HTML]{9FC5E8}}c 
  >{\columncolor[HTML]{F9CB9C}}c 
  >{\columncolor[HTML]{D9D2E9}}c }
  \cline{1-1}
  \multicolumn{1}{|c|}{\cellcolor[HTML]{F1C232}threshold} &
    \cellcolor[HTML]{6AA84F}match\% &
    \cellcolor[HTML]{3C78D8}c.c match\% &
    \cellcolor[HTML]{E69138}limit match\% &
    \cellcolor[HTML]{8E7CC3}corruption rate \\ \cline{1-1}
  0.000 & 1.000 & 1.000 & 0.984 & 0.000 \\
  0.025 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.050 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.075 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.100 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.125 & 0.406 & 1.000 & 0.391 & 0.000 \\
  0.150 & 0.400 & 1.000 & 0.385 & 0.000 \\
  0.175 & 0.386 & 1.000 & 0.371 & 0.000 \\
  0.200 & 0.364 & 1.000 & 0.348 & 0.000 \\
  0.225 & 0.335 & 1.000 & 0.319 & 0.000 \\
  0.250 & 0.298 & 1.000 & 0.282 & 0.000 \\
  0.275 & 0.253 & 1.000 & 0.237 & 0.000 \\
  0.300 & 0.201 & 1.000 & 0.185 & 0.000 \\
  0.325 & 0.158 & 1.000 & 0.142 & 0.000 \\
  0.350 & 0.125 & 0.944 & 0.110 & 0.028 \\
  0.375 & 0.100 & 0.944 & 0.085 & 0.028 \\
  0.400 & 0.080 & 0.944 & 0.065 & 0.028 \\
  \cellcolor[HTML]{FF0000}0.425 &
    \cellcolor[HTML]{FF0000}0.054 &
    \cellcolor[HTML]{FF0000}0.889 &
    \cellcolor[HTML]{FF0000}0.040 &
    \cellcolor[HTML]{FF0000}0.057 \\
  0.450 & 0.043 & 0.889 & 0.029 & 0.057 \\
  0.475 & 0.034 & 0.778 & 0.022 & 0.118 \\
  0.500 & 0.025 & 0.778 & 0.013 & 0.118 \\
  0.525 & 0.023 & 0.778 & 0.010 & 0.118 \\
  0.550 & 0.020 & 0.667 & 0.010 & 0.184 \\
  0.575 & 0.019 & 0.667 & 0.009 & 0.184 \\
  0.600 & 0.016 & 0.556 & 0.007 & 0.255 \\
  0.625 & 0.014 & 0.556 & 0.005 & 0.255 \\
  0.650 & 0.014 & 0.556 & 0.005 & 0.255 \\
  0.675 & 0.006 & 0.222 & 0.003 & 0.529 \\
  0.700 & 0.003 & 0.111 & 0.001 & 0.667 \\
  0.725 & 0.001 & 0.000 & 0.001 & 1.000 \\
  0.750 & 0.001 & 0.000 & 0.001 & 1.000 \\
  0.775 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.800 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.825 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.850 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.875 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.900 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.925 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.950 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.975 & 0.000 & 0.000 & 0.000 & 1.000 \\
  1.000 & 0.000 & 0.000 & 0.000 & 1.000
  \end{tabular}
  \end{table}

\begin{figure}[h]
    \caption{match metrics vs threshold used}\label{fig:match_metrics_vs_threshold_used}
    \centering
    \includegraphics[height=0.5\textwidth]{pictures/match_metrics_vs_threshold_used.png}
\end{figure}

Assuming the algorithm has to solve a 500 piece puzzle, with a limit match\% of 0.04
and a corruption rate of 0.057 (data taken from the line in red);
what would this mean in terms of accuracy of the results?

@@

  \item \textbf{Possible Combinations:}\newline
  A puzzle with N pieces can be put together in many different ways,
  (even if not all of 	them actually fit together).
  The total number of possible combinations is \(N! \times 4^N\) where
  \(N!\) represent all possible way to combinate the pieces in a particular position, and
  \(4^N\) represents all possible orientations that each piece can have.
  \item \textbf{Possible Correct Combination:}\newline
  Is one of the possible combinations where all the connections are considered a match
  by the comparing algorithm.
  \item \textbf{Actual Correct Combination:}\newline
  An Actual Correct Combination is a Possible Combination that
  is also the correct solution of the original puzzle	
\end{itemize}

@@

From the graph \ref{fig:GCL_Corruption_Rate}, it can be observed that with a corruption rate of 0.057,
a neighbors comparison value of about 80\%
can be expected. Which means that one in every 5 connections on average will be wrong.
So in a puzzle of 500 pieces (which has approximately 1000 connections),
200 connections will be wrong on average.
It is fair to say that this is not an ideal result.

\subsubsection{Limit Match\% Analysis}
As seen earlier, the limit match percentage is \(4\%\).\newline \newline
Given that in a puzzle of N pieces there are around \(2N \) connections,
the probability of one random combination to be a
possible correct combination is: \(0.054^{2N}\).\newline \newline
The total number of possible combinations are \(N! \times 4^N\),
which means that on average, on a puzzle with \(N\) pieces,
there will be \(0.054^{2N} \times N! \times 4^N \)
possible correct combinations.\newline \newline
For \( N = 500 \) the expected number of possible combinations is around \( 1.5 \times 10^{37} \).
Which makes the chance of finding the actual correct combination basically zero.
\subsubsection{Conclusion}
In this case both the match\% and the corruption rate are bad enough to make a correct reconstruction impossible.
To lower the limit match\% is necessary to increase the threshold, but this would increase the corruption rate.
To lower the corruption rate is necessary to decrease the threshold, but this would increase the limit match\%.
This means that, regardless of the threshold chosen, our comparison algorithm \ref{document:my_comparator}
can not work with a state of the art solver \ref{document:GCL}.

@@

There are two way to solve this deadlock:

@@

Improving the comparator can shortly be done.
Some minor improvements can be made by spending some time tweaking the current algorithm.
But it is clear that, for such a task,
the optimal solution is probably to use machine learning.

@@

Different algorithms have different resilience to corrupted data.
All the major algorithms that have been proposed since now, focus on speed.
It is possible that an algorithm that focuses on accuracy over speed
could work with our comparator.

@@

Improving the comparator is probably the best long term solution,
but it comes with a problem:\newline
Manually testing if some pieces fit together, then making a scan, and finally label
them to create a dataset would require hundreds if not thousands of hours.

On the other hand improving the solver is not a good solution long term,
given that it will almost certainly have a worst time complexity,
but could have some major short term benefit.

In particular it does not require to create a huge dataset,
and could be used to build one.
In Fact it could solve hundreds of small puzzles,
and automatically label the connections using the solution he created.

Given the two options, the author of this paper has chosen to focus on improving
the solver algorithm. The choice was driven by the belief that creating a new algorithm,
for then using that to build a dataset,
would still be faster compared to building a dataset manually.

\section{The Solver}\label{document:my_solver}
The Solver that has been created is not the main focus of this paper,
and cannot be considered state-of-the-art if compared with the current best
digital puzzle solver. But can probably be considered so if compared with current
``real world'' puzzle Solvers.z

@@

\begin{table}[H]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{D9EAD3}}c 
  >{\columncolor[HTML]{D0E0E3}}c 
  >{\columncolor[HTML]{E6B8AF}}c 
  >{\columncolor[HTML]{FCE5CD}}c }
  \cellcolor[HTML]{B6D7A8} &
    \cellcolor[HTML]{A2C4C9} &
    \multicolumn{2}{c}{\cellcolor[HTML]{EA9999}Execution time {[}s{]}} \\
  \multirow{-2}{*}{\cellcolor[HTML]{B6D7A8}Size} &
    \multirow{-2}{*}{\cellcolor[HTML]{A2C4C9}Pieces} &
    \cellcolor[HTML]{DD7E6B}Digital puzzle &
    \cellcolor[HTML]{F9CB9C}Real Puzzle \\
  4x4   & 16  & 4   & 59   \\
  8x8   & 64  & 30  & 2851 \\
  16X16 & 256 & 377 & N/A 
  \end{tabular}
\end{table}

>>>>

\subsection{Splitting The Pieces}

As introduced in section~\ref{document:splitter},  the initial stage in puzzle solving involves
splitting an image composed of many pieces into individual ones.
This is relatively straightforward, and can be done with the following steps:

\begin{itemize}
  \item Apply a threshold and transform an RGB image into a binary mask.
  \item Find all individual Blobs
  (a Blob is defined as a set of connected pixels with the same color) and for each one:

@@

The next step following the general structure~\ref{document:splitter}
is to split a piece into
his 4 sides, this could be done with the following steps:

@@

  \item \textbf{Remove the holes from the piece:}\newline
  To remove the holes from the piece, the program employs a three-step process. Initially it
  computes the convex hull of the piece~\ref{fig:s_s_ch}.
  Subsequently it calculates the difference between the convex hull and the original image,
  resulting in an ``image with filler areas''~\ref{fig:fig:s_s_og_minus_ch}.
  It can be noted that these filler areas have distinct shapes,
  depending on what has generated them (either a ``hole'' or a ``knob'').
  Therefore they can be categorized.
  Finally the filler areas are added back to the only if
  they originated from a hole. This results in an image where the holes
  have been filled~\ref{fig:s_s_no_holes}

  \item \textbf{Remove the knobs from he piece:}\newline
  In order to remove the knobs from the piece, the image without holes
  undergoes an erosion~\ref{fig:s_s_erosion} followed by a dilation~\ref{fig:s_s_dilatation}.
  This process results in an image that resembles the original, but without any knobs.
  Subsequently, the program identifies the pixels that are white in the image without holes~\ref{fig:s_s_no_holes},
  but not in the eroded and dilated version~\ref{fig:s_s_dilatation}.
  This leads to the formation of a set of blobs ~\ref{fig:s_s_no_holes_minus_expansion}.
  It is important to note that the shape of a blob can vary significantly depending on whether it originated
  from an ``angle'' or a ``knob'' and thus they can be classified accordingly.
  Following this, the program proceeds to eliminate from the hole-free
  image all pixels that are in close proximity to a blob generated by a knob.
  This operation yields an image that is both devoid of knobs and holes~\ref{fig:s_s_no_knobs}.

  \item \textbf{Find the coordinates of the four corners:}\newline
  In order to determine the coordinates of the corners,
  the program employs a three-step approximation method.
  Initially, it identifies the minimum enclosing rectangle and
  utilizes the coordinates of its corners
  as the first approximation~\ref{fig:s_s_min_enc_rec}.\newline
  For the second approximation, the program selects,
  from the white pixels in close proximity to the first approximation,
  the pixel that contains the highest number of black pixels
  within a specified range.
  Then it considers only the pixels that are within a certain
  distance of the second approximation, and finds the minimum
  enclosing triangle of sed pixels~\ref{fig:s_s_min_enc_triangle}.\newline
  The corner of the triangle that is nearest to the second
  approximation serves as the third and final approximation
  for the corner of the puzzle piece.
  The position of the four corners can be seen in image~\ref{fig:s_s_corners_found}.

  \item \textbf{Split each piece into four sides using the previously found coordinates:}\newline
	After the program has successfully identified the four corner coordinates,
  it can straightforwardly derive each of the four sides.
  An example of a single side can be seen in image F4l.~\ref{fig:s_s_a_piece_side}.
\end{itemize}

@@

\subsection{Comparing The Sides}\label{document:my_comparator}
The last step in the setup, is to compare the sides that have been
generated before.\newline
In order to generate a compatibility shore,
the program compute the following steps:

\begin{itemize}
  \item For each side, it considers only the border, and  makes it thicker.
  \item It puts two sides attached to each other using the coordinates of the corners (In the same way a human would do to test if two pieces fit together).
  \item It calculates the “Or Area”; that is, the number of pixels that belong to the border of one side or the other.
  \item It calculates the “And Area”; that is, the number of pixels that belong to the border of both sides.
  \item It calculates the final shore, which is defined as: \(Shore = \frac{And \space Area}{Or \space Area}\), and goes from 0 to 1.
\end{itemize}

@@

\section{Applying Already Existing Algorithms To The Real World}
With the initial setup completed, it is now possible to
test the existing algorithms with real-world puzzle. For this test,
the fist algorithm~\ref{document:GCL} is selected due to the comprehensive
details provided in the paper. Notably, it contains information
regarding the algorithm's accuracy in relation to the corruption rate,
which is crucial for this analysis.

The conducted tests reveal that the Comparator developed in this paper~\ref{document:my_comparator}
and the "Graph Connection Laplacian" solution ~\ref{document:my_comparator} are not compatible with each other.
A formal proof supporting this assertion is presented subsequently.

@@

The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\ref{document:GCL} takes as input a binary value.
Which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.
\subsubsection{Input Data}
To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:

\begin{itemize}
  \item \textbf{match\%:}\newline
  The probability that 2 randomly selected sides matches.

  \item \textbf{correct combination match\% (or c.c match\%):}\newline
  The probability that 2 randomly selected sides matches given that in the correct puzzle
  solution they are actually close to each other. Ideally this should be 1.

  \item \textbf{limit match\%:}\newline
  Given that this measure has been taken on a 16 piece puzzle,
  the match\% is highly influenced by the correct piece matching together.
  With a bigger puzzle the match\% would be lower (Given that the amount
  of correct couple of sides scales with N, while the amount of
  possible couple of sides scales with \(N^2\). Where N is the number of pieces).\newline
  Limit match\% is an approximation of what the match\%
  would be in the limit for \(N \rightarrow + \infty\).
  This value is obtained by subtracting to match\%
  the probability of choosing randomly the correct side,
  multiplied by the probability that the comparison returns true
  (which is c.c match\%). \newline
  Ideally limit match\% should be almost zero.
  \[limit \: math\% = math\% - \frac{c.c. \: mathc\%}{16 \times 4}\]

  \item \textbf{corruption rate:}\newline
  Is defined as: \(1-\sqrt{c.c \: match\%}\). Ideally this should be 0.

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[H]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{FFE599}}c 
  >{\columncolor[HTML]{B6D7A8}}c 
  >{\columncolor[HTML]{9FC5E8}}c 
  >{\columncolor[HTML]{F9CB9C}}c 
  >{\columncolor[HTML]{D9D2E9}}c }
  \cline{1-1}
  \multicolumn{1}{|c|}{\cellcolor[HTML]{F1C232}threshold} &
    \cellcolor[HTML]{6AA84F}match\% &
    \cellcolor[HTML]{3C78D8}c.c match\% &
    \cellcolor[HTML]{E69138}limit match\% &
    \cellcolor[HTML]{8E7CC3}corruption rate \\ \cline{1-1}
  0.000 & 1.000 & 1.000 & 0.984 & 0.000 \\
  0.025 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.050 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.075 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.100 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.125 & 0.406 & 1.000 & 0.391 & 0.000 \\
  0.150 & 0.400 & 1.000 & 0.385 & 0.000 \\
  0.175 & 0.386 & 1.000 & 0.371 & 0.000 \\
  0.200 & 0.364 & 1.000 & 0.348 & 0.000 \\
  0.225 & 0.335 & 1.000 & 0.319 & 0.000 \\
  0.250 & 0.298 & 1.000 & 0.282 & 0.000 \\
  0.275 & 0.253 & 1.000 & 0.237 & 0.000 \\
  0.300 & 0.201 & 1.000 & 0.185 & 0.000 \\
  0.325 & 0.158 & 1.000 & 0.142 & 0.000 \\
  0.350 & 0.125 & 0.944 & 0.110 & 0.028 \\
  0.375 & 0.100 & 0.944 & 0.085 & 0.028 \\
  0.400 & 0.080 & 0.944 & 0.065 & 0.028 \\
  \cellcolor[HTML]{FF0000}0.425 &
    \cellcolor[HTML]{FF0000}0.054 &
    \cellcolor[HTML]{FF0000}0.889 &
    \cellcolor[HTML]{FF0000}0.040 &
    \cellcolor[HTML]{FF0000}0.057 \\
  0.450 & 0.043 & 0.889 & 0.029 & 0.057 \\
  0.475 & 0.034 & 0.778 & 0.022 & 0.118 \\
  0.500 & 0.025 & 0.778 & 0.013 & 0.118 \\
  0.525 & 0.023 & 0.778 & 0.010 & 0.118 \\
  0.550 & 0.020 & 0.667 & 0.010 & 0.184 \\
  0.575 & 0.019 & 0.667 & 0.009 & 0.184 \\
  0.600 & 0.016 & 0.556 & 0.007 & 0.255 \\
  0.625 & 0.014 & 0.556 & 0.005 & 0.255 \\
  0.650 & 0.014 & 0.556 & 0.005 & 0.255 \\
  0.675 & 0.006 & 0.222 & 0.003 & 0.529 \\
  0.700 & 0.003 & 0.111 & 0.001 & 0.667 \\
  0.725 & 0.001 & 0.000 & 0.001 & 1.000 \\
  0.750 & 0.001 & 0.000 & 0.001 & 1.000 \\
  0.775 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.800 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.825 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.850 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.875 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.900 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.925 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.950 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.975 & 0.000 & 0.000 & 0.000 & 1.000 \\
  1.000 & 0.000 & 0.000 & 0.000 & 1.000
  \end{tabular}
  \end{table}

\begin{figure}[H]
    \caption{match metrics vs threshold used}\label{fig:match_metrics_vs_threshold_used}
    \centering
    \includegraphics[height=0.5\textwidth]{pictures/match_metrics_vs_threshold_used.png}
\end{figure}

Now, let's consider Algorithm \ref{document:GCL} tasked with solving a 500-piece puzzle
using our Comparator \ref{document:my_comparator}.
A threshold of 0.425 is chosen;
This implies a imit match\% of 0.04 and a corruption rate of 0.057.
What would this mean in terms of accuracy of the results?

@@

  \item \textbf{Possible Combinations:}\newline
  A puzzle with N pieces can be put together in many different ways,
  (Even if not all of 	them actually fit together).
  The total number of possible combinations is \(N! \times 4^N\) where
  \(N!\) represent all possible way to combinate the pieces in a particular position, and
  \(4^N\) represents all possible orientations that each piece can have.
  \item \textbf{Possible Correct Combination:}\newline
  Is one of the possible combinations where all the connections are considered a match
  by the comparing algorithm.
  \item \textbf{Actual Correct Combination:}\newline
  An Actual Correct Combination is a Possible Combination that
  is also the correct solution of the original puzzle	
\end{itemize}

@@

In Figure \ref{fig:GCL_Corruption_Rate}, it can be observed that at a corruption rate of 0.057,
a neighbors comparison metric of roughly 80\% can be anticipated.
This implies that, on average, one out of every five connections will be incorrect.
In the context of a puzzle comprising 500 pieces (equating to approximately 1000 connections),
an estimated 200 connections will be inaccurate on average.
It is reasonable to assert that this outcome is suboptimal.

\subsubsection{Limit Match\% Analysis}
Let's remember that \(limit\_match\% = 0.04\).

Given that in a puzzle with N pieces there are around \(2N \) connections,
the probability of one random combination to be a
possible correct combination is: \(0.04^{2N}\).

The total number of possible combinations are \(N! \times 4^N\),
which means that on average, in a puzzle with \(N\) pieces,
there will be \(0.04^{2N} \times N! \times 4^N \)
possible correct combinations.

For \( N = 500 \) the expected number of possible combinations is around \( 1.5 \times 10^{37} \).
Which makes the chance of finding the actual correct combination basically zero.
\subsubsection{Conclusion}
In this case both the match\% and the corruption rate are bad enough to make a correct reconstruction impossible.
To lower limit match\% is necessary to increase the threshold, but this would increase the corruption rate.
To lower the corruption rate is necessary to decrease the threshold, but this would increase the limit match\%.
This means that, regardless of the threshold chosen, our comparison algorithm \ref{document:my_comparator}
can not work with a state of the art solver \ref{document:GCL}.

@@

There are two viable approaches to overcome this challenge.
It is either necessary to enhance the Comparator while continuing
to utilize the state-of-the-art solver,
or it is possible to re-design the solver algorithm and create one
specifically designed to operate with noisier data.

@@

Improving the comparator can shortly be done.
Some minor improvements can be made by spending some time
tweaking the current algorithm.
However, it is evident that for a task of this nature,
the most viable solution would likely involve
leveraging machine learning techniques.

@@

The puzzle dilemma is a ``multiobjective optimization problem'',
where one objective is optimizing the time complexity,
and the other is optimizing the accuracy of the algorithm
in the presence of corrupted data.
All the major algorithms proposed up to this point have prioritize speed.
However, it is conceivable, and even probable,
that an algorithm prioritizing accuracy over speed could prove
effective with our comparator

@@

Improving the comparator is likely the most effective long-term solution,
but it presents a significant challenge: manually testing if certain
pieces fit together, followed by scanning and labeling,
is a time-intensive process that could require hundreds,
if not thousands, of hours.

On the other hand, improving the solver may not be the optimal long-term
solution, as it is likely to result in a worse time complexity.
However, it could yield significant short-term benefits.

Notably, this approach does not necessitate the creation of an extensive dataset
and has the potential to facilitate its development.
In fact, it could have the capability to solve numerous small
puzzles and subsequently auto-label the connections
based on the solutions it generates.

Given the two options, it has been decided to focus on improving
the solver algorithm. This choice was driven by the belief
that creating a new algorithm, and subsequently using it to
generate a dataset, would still be a more time-efficient
approach compared to manually constructing a dataset.

\section{The Solver}\label{document:my_solver}
The Solver that has been created is not the main focus of this paper,
and cannot be considered state-of-the-art if compared with the current best
digital puzzle solver. But can probably be considered so if compared with current
``real world'' puzzle Solvers.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{D9EAD3}}c 
  >{\columncolor[HTML]{D0E0E3}}c 
  >{\columncolor[HTML]{E6B8AF}}c 
  >{\columncolor[HTML]{FCE5CD}}c }
  \cellcolor[HTML]{B6D7A8} &
    \cellcolor[HTML]{A2C4C9} &
    \multicolumn{2}{c}{\cellcolor[HTML]{EA9999}Execution time {[}s{]}} \\
  \multirow{-2}{*}{\cellcolor[HTML]{B6D7A8}Size} &
    \multirow{-2}{*}{\cellcolor[HTML]{A2C4C9}Pieces} &
    \cellcolor[HTML]{DD7E6B}Digital puzzle &
    \cellcolor[HTML]{F9CB9C}Real Puzzle \\
  4x4   & 16  & 4   & 59   \\
  8x8   & 64  & 30  & 2851 \\
  16x16 & 256 & 377 & N/A 
  \end{tabular}
\end{table}
